Synthesizing Quotient Lenses

### 2018-03-14 papers/QuotientLenses/main.tex
minor responses to things in section 5

This rule essentially says that the composition $q_1 \; ; \; q_2$ is
well defined if and only if the intermediary QREs $Q_3$ and $Q_4$ define the
same equivalence relation on regular languages that are equivalent modulo the
star-semiring axioms\bcp{No: the regular expressions are equivalent modulo
  these axioms; the regular {\em languages} are
  identical}. (See~\cite[\S 4]{quotientlenses} for an example of what goes
wrong if this premise is dropped.\bcp{Didn't we used to have a discussion
  about how implementing this rule is hard because it involves checking
  language equivalence so we follow Boomerang's rule?  I think this is
  important to mention because this was a significant restriction on the
  power of composition in Boomerang.  It doesn't apply here (right?) because
we intend to synthesize these lenses, not write them by hand, so we will
never actually need to typecheck a functional composition expression.}) The
condition $\mathcal{L}(W(Q_2)) = \mathcal{L}(W(Q_3))$ 
says that the intermediary language is the same on both sides, while the
condition $K(Q_2) \equiv^s K(Q_3)$ says that the kernel regular expressions are
equivalent modulo the star-semiring axioms. Finally, the condition
$\canonize(Q_2) = \canonize(Q_3)$ says that $Q_2$ and $Q_3$ define the same
equivalence relation on $\mathcal{L}(W(Q_2))= \mathcal{L}(W(Q_3))$.

>>>>

This rule essentially says that the composition $q_1 \; ; \; q_2$ is well
defined if and only if the intermediary QREs $Q_3$ and $Q_4$ define the same
equivalence relation on regular expressions that are equivalent modulo the
star-semiring axioms. (See~\cite[\S 4]{quotientlenses} for an example of what
goes wrong if this premise is dropped.\bcp{Didn't we used to have a discussion
  about how implementing this rule is hard because it involves checking language
  equivalence so we follow Boomerang's rule? I think this is important to
  mention because this was a significant restriction on the power of composition
  in Boomerang. It doesn't apply here (right?) because we intend to synthesize
  these lenses, not write them by hand, so we will never actually need to
  typecheck a functional composition expression.}\afm{Boomerang does check
  language equivalence, we restrict the check to star-semiring equivalence
  because we aren't complete when we allow arbitrary equivalence.}) The
condition $\mathcal{L}(W(Q_2)) = \mathcal{L}(W(Q_3))$ says that the intermediary
language is the same on both sides, while the condition $K(Q_2) \equiv^s K(Q_3)$
says that the kernel regular expressions are equivalent modulo the star-semiring
axioms. Finally, the condition $\canonize(Q_2) = \canonize(Q_3)$ says that $Q_2$
and $Q_3$ define the same equivalence relation on $\mathcal{L}(W(Q_2))=
\mathcal{L}(W(Q_3))$.
